---
title: "SEM_Script"
author: "Alex Rogers"
date: "2024-08-14"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading in data and dependencies

```{r}
#loading dependencies
library(dplyr)
library(lme4)
library(lmerTest)
library(sjPlot)
library(lavaan)
library(semPlot)
library(tidyverse)
library(lavaanPlot)

#loading in data
df <-read.csv("bard_ratings.csv")
df <- df %>%
  mutate(bard = ifelse(bardguilt == TRUE, 1, 0))


#cleaning data
df_z <- df %>%
  mutate(z_episodic = ((recall-mean(recall))/sd(recall)),
         z_semantic = ((know-mean(know))/sd(know)),
         z_realism = ((realrate-mean(realrate))/sd(realrate)),
         z_case_strength = ((rating-mean(rating))/sd(rating)))
#View(df_z)
```

## Setting up model 1

Question: Do memory and realism load onto a common factor?

# CFA clustering by subject - Are the memory questions comprised of a common memory factor? 
```{r}
model_clust <- '
  Memory =~ z_episodic + z_semantic + z_realism
  '

#fitting model by setting factor variance to 1
fit_clust <- cfa(model_clust, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "num_uid")

# viewing results
summary(fit_clust, fit.measures=TRUE,standardized=TRUE)


# Quick plot of the model - standardized loadings
semPaths(fit_clust, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```

# clustering by subject for memory predicting case strength

```{r}

model_c <- '
  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  z_case_strength ~ z_realism'

fit_c <-sem(model_c, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "num_uid")

# viewing results
summary(fit_c, fit.measures=TRUE,standardized=TRUE)

# Quick plot of the model - standardized loadings
semPaths(fit_c, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")

```

#SEM only general factor predicting case strength 

```{r}
model_sem_gen <- '
  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  '

#fitting model by setting factor variance to 1
fit_gen <- cfa(model_sem_gen, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "num_uid")

# viewing results
summary(fit_gen, fit.measures=TRUE,standardized=TRUE)


# Quick plot of the model - standardized loadings
semPaths(fit_gen, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```



# Model Comparison 

```{r}
anova(fit_gen, fit_c)
```

# General memory factor predicting case strength + allowing percieved realism to directly predict case strength rating

This is only clustering observations by subject.   

```{r}
model_scen_sem <- '

  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  z_case_strength ~ z_realism'

#fitting model by setting factor variance to 1
fit_scen_sem <- sem(model_scen_sem, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "num_uid")

# viewing results
summary(fit_scen_sem, fit.measures=TRUE,standardized=TRUE)

# Quick plot of the model - standardized loadings
semPaths(fit_scen_sem, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```
# Compare with model that allows direct paths from semantic or episodic 

```{r}
model_alt_semantic <- '

  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  z_case_strength ~ z_semantic'

#fitting model by setting factor variance to 1
fit_alt_semantic <- sem(model_alt_semantic, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "num_uid")

# viewing results
summary(fit_alt_semantic, fit.measures=TRUE,standardized=TRUE)

# Quick plot of the model - standardized loadings
semPaths(fit_alt_semantic, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```

```{r}
model_alt_episodic <- '

  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  z_case_strength ~ z_episodic'

#fitting model by setting factor variance to 1
fit_alt_episodic <- sem(model_alt_episodic, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "num_uid")

# viewing results
summary(fit_alt_episodic, fit.measures=TRUE,standardized=TRUE)

# Quick plot of the model - standardized loadings
semPaths(fit_alt_episodic, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```

# SCENARIO - General memory factor predicting case strength + allowing percieved realism to directly predict case strength rating

This is only clustering observations by scenario.   


```{r}
scenario_model_sem_gen <- '
  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  '

#fitting model by setting factor variance to 1
scenario_fit_gen <- cfa(model_sem_gen, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "scenario")

# viewing results
summary(scenario_fit_gen, fit.measures=TRUE,standardized=TRUE)


# Quick plot of the model - standardized loadings
semPaths(scenario_fit_gen, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```



```{r}
model_scenario_sem <- '

  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  z_case_strength ~ z_realism'

#fitting model by setting factor variance to 1
fit_scenario_sem <- sem(model_scen_sem, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "scenario")

# viewing results
summary(fit_scenario_sem, fit.measures=TRUE,standardized=TRUE)

# Quick plot of the model - standardized loadings
semPaths(fit_scenario_sem, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```

# model comparison 

```{r}
anova(scenario_fit_gen, fit_scenario_sem)
```


```{r}
scenario_model_alt_semantic <- '

  Memory =~ z_episodic + z_semantic + z_realism
  z_case_strength ~ Memory
  z_case_strength ~ z_semantic'

#fitting model by setting factor variance to 1
scenario_fit_alt_semantic <- sem(model_alt_semantic, data=df_z, meanstructure=TRUE, missing="ML", std.lv = TRUE, cluster = "scenario")

# viewing results
summary(scenario_fit_alt_semantic, fit.measures=TRUE,standardized=TRUE)

# Quick plot of the model - standardized loadings
semPaths(scenario_fit_alt_semantic, intercept = FALSE, whatLabel = "std", nCharNodes = 0,
          residuals = TRUE, exoCov = FALSE)
 mtext("*Factor loadings are presented at the standardized level", side = 1, line = 4, family = "Times New Roman")
```

